Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-05-05 tensor/draft/draft-tensor-op.tex
[tensor/draft] Update uncertainty plots
* rescale J_* by B meson lifetime
* increase font size
* expand figure caption

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
  }
  \label{fig:FHvsCT}
\end{figure*}

>>>>

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ \eos{The sensitivity to the tensorial coupling
      $\wilson{T}$ of $F_H$ [first row], ${\cal B}$ [second row] for
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ for $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      rations. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.}  }
  \label{fig:FHvsCT}
\end{figure*}
